National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-18 Analysis.Rmd
jb finished first pass at re-write. To do: - ben to polish - jb and ben to redo revision letter. - ben to assimilate futher comments to overleaf draft - jb to remind ben to push to github from overleaf

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : "html_document" 
editor_options: 
  chunk_output_type: console
---

@@

# Methods
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
We used `r cite_r("r-references.bib")` for all our analyses.

>>>>

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["b-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : "html_document" 
editor_options: 
  chunk_output_type: console
---

@@

```{r, sessioninfo, include=FALSE}

citation(package = "base", lib.loc = "/Users/josephbulbulia/Dropbox/BIBS")
toLatex(sessionInfo(), locale = FALSE)
sapply(names(sessionInfo()$otherPkgs), function(x) print(citation(x), style = "Bibtex"))

out <- sapply(names(sessionInfo()$otherPkgs),
              function(x) print(citation(x), style = "Bibtex"))
print(out)
```

# Methods
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
We used `r cite_r("b-references.bib")` for all our analyses.

### 2020-11-18 Manuscript.Rmd
jb finished first pass at re-write. To do: - ben to polish - jb and ben to redo revision letter. - ben to assimilate futher comments to overleaf draft - jb to remind ben to push to github from overleaf

---
title             : "National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs"
shorttitle        : "Longitudinal Wellbeing from Spiritual Beliefs"
author: 
  - name          : "Ben Highland"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "benhighland6420@gmail.com"
  - name          : "Everett L. Worthington"
    affiliation   : "2"
    institution   : "Department of Psychology Virginia Commonwealth University"
  - name          : "Don E Davis"
    affiliation   : "3"
    institution   : "Department of Psychology Georgia State University"
  - name          : "Chris G. Sibley"
    affiliation   : "4"
    institution   : "School of Psychology University of Auckland"
  - name          : "Joseph Bulbulia"
    affiliation   : "5"
    institution   : "School of Psychology Victoria University"

@@

keywords          : "Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being"
wordcount         : "5015"
bibliography      : ["b-references.bib"]

@@

Because missing values can result in biased estimates [@Blackwell2017-oq], we multiply imputed 10 datasets using the AmeliaII package in R[@Honaker2011-yu].  We conducted a parallel analysis averaging over the multiply imputed datasets, without any substantive difference to inferences.

@@

```{r fig.cap = "Combination Coefficient Plots for Personal Well-being and Life Satisfaction Spirit Belief Longitudinal Models"}
knitr::include_graphics("Figs/USEcoefficientplots-1.png")
```

@@

# Supplemental Material
Statistical analysis was performed using R version 3.6.1 (2019-07-05). Platform: x86_64-w64-mingw32 (64-bit), running under: Windows 10 (Action of the Toes). Generalized Linear Mixed Models were generated using the glmmTMB (Brooks et al. 2017; Knowles and Frederick 2019) package in R. In addition, we used the following R packages: dplyr (Hadley Wickham et al. 2019), tidyr (H. Wickham and Henry 2019), sjPlot (D. Lüdecke 2020), ggeffects (Daniel Lüdecke 2018), table1  and their dependencies.
Tables and coefficient plots were generated using the glmmTMB, ggeffects, and sjPlot packages in R. Models for both subjective well-being variables used family = gaussian, assuming a normal distribution. We ran each individual’s unique ID as a random-effect. The tab_model and plot_model commands in sjPlot allowed for the creation of tables and coefficient plots. Predicted probability plots were generated using the ggpredict command in the ggeffects package. The table1 package in R was used for the creation of descriptive statistics tables.

>>>>

---
title             : "National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs"
shorttitle        : "Longitudinal Wellbeing from Spiritual Beliefs"
author: 
  - name          : "Ben Highland"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Ben's Postal address"
    email         : "benhighland6420@gmail.com"
  - name          : "Everett L. Worthington"
    affiliation   : "2"
    institution   : "Department of Psychology Virginia Commonwealth University"
  - name          : "Don E Davis"
    affiliation   : "3"
    institution   : "Department of Psychology Georgia State University"
  - name          : "Chris G. Sibley"
    affiliation   : "4"
    institution   : "School of Psychology University of Auckland"
  - name          : "Joseph Bulbulia"
    affiliation   : "5"
    institution   : "School of Psychology Victoria University"

@@

keywords          : "Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being"
wordcount         : "5269 words in text body, 1078 words in reference section"
bibliography      : ["b-references.bib"]

@@

### System and packages
The analysis was performed using R version 4.0.2 (2020-06-22). The Platform was x86_64-apple-darwin17.0 (64-bit) Running under: macOS Catalina 10.15.6
We are greatful to the contributors and mantainers of the following packages:
R [Version 4.0.2; @R-base] and the R-packages *Amelia* [Version 1.7.6; @R-Amelia], *citr* [Version 0.3.2; @R-citr], *dplyr* [Version 1.0.2; @R-dplyr], *equatiomatic* [Version 0.1.0.9000; @R-equatiomatic], *forcats* [Version 0.5.0; @R-forcats], *ggeffects* [Version 0.15.0; @R-ggeffects], *gghighlight* [Version 0.3.0; @R-gghighlight], *ggplot2* [Version 3.3.2; @R-ggplot2], *ggsci* [Version 2.9; @R-ggsci], *lme4* [Version 1.1.23; @R-lme4], *Matrix* [Version 1.2.18; @R-Matrix], *papaja* [Version 0.1.0.9997; @R-papaja], *parameters* [Version 0.8.6.1; @R-parameters], *patchwork* [Version 1.0.1; @R-patchwork], *prettycode* [Version 1.1.0; @R-prettycode], *purrr* [Version 0.3.4; @R-purrr], *Rcpp* [Version 1.0.5.1; @R-Rcpp_a; @R-Rcpp_b], *readr* [Version 1.3.1; @R-readr], *report* [Version 0.1.0; @R-report], *see* [Version 0.5.2.1; @R-see], *sjPlot* [Version 2.8.4; @R-sjPlot], *stringr* [Version 1.4.0; @R-stringr], *styler* [Version 1.3.2; @R-styler], *table1* [Version 1.2; @R-table1], *texreg* [Version 1.37.5; @R-texreg], *tibble* [Version 3.0.4; @R-tibble], *tidyr* [Version 1.1.2; @R-tidyr], and *tidyverse* [Version 1.3.0; @R-tidyverse]"

### Missing data
Because missing values can result in biased estimates [@Blackwell2017-oq], we multiply imputed 10 datasets using the AmeliaII package in R[@Honaker2011-yu].We conducted a parallel analysis averaging over the multiply imputed datasets, without any substantive difference to inferences. Details of this analysis can be found at: https://github.com/jacopastorius/nzavs_spiritbeliefWellbeing.

@@

```{r fig.cap = "Combination Coefficient Plots for Personal Well-being and Life Satisfaction Spirit Belief Longitudinal Models"}
knitr::include_graphics("Figs/USE_2_coefficientplots-1.png")
```

@@
